---
title: "Clean Kcnh2 script"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Perform pdb.blast() on the human kcnh2 sequence obtained via accession number

```{r, warning=FALSE, message=FALSE}
library(bio3d)
human.seq <- "AAI27674.1"
kcnh2.pdb <- blast.pdb(human.seq)
```

Trim down the blast.pdb object to contain only the pdb ids and evalues

```{r}
kcnh2.pdb.trim <- kcnh2.pdb$hit.tbl[ , c("identity", "s.end")]
head(kcnh2.pdb.trim)
```

Call pdb.annotate() on the human kcnh2 sequence; select the desired data columns

```{r, warning=FALSE}
pdb.ids <- kcnh2.pdb$hit.tbl$subjectids
kcnh2.anno <- pdb.annotate(pdb.ids, anno.terms = c("structureId", 
                                                     "experimentalTechnique",
                                                     "source",
                                                     "resolution"))
rownames(kcnh2.anno) <- kcnh2.anno$structureId
kcnh2.anno <- kcnh2.anno[, -1]

head(kcnh2.anno)
```

Bind the anno and trimmed matrices together

```{r, message=FALSE}
kcnh2.full.anno <- cbind(kcnh2.anno, kcnh2.pdb.trim)
head(kcnh2.full.anno)
```

Select three unique hits

```{r}
pdb.unique <- kcnh2.full.anno[c("5VA1", "5K7L", "5U6O"), ]
pdb.unique
```

## Rename columns to reflect evalue

```{r, results='asis'}
colnames(pdb.unique) <- c( "experimentalTechnique", 
                           "source",
                           "resolution",
                           "identity",
                           "evalue")
                           


knitr::kable(pdb.unique, 
             caption = "Annotated Parameters of Unique PDB Hits", 
             align = 'l')
```

Generate a pdb object of 5VA1 structure for display in VMD

```{r, message=FALSE}
hum.kcnh2.str <- read.pdb("5VA1")
write.pdb(hum.kcnh2.str, file = "5VA1_str")
```

